---
geometry       : vmargin=1.0in, hmargin=0.75in
bibliography   : ../bib/span585.bib
csl            : ../bib/apa.csl
output:
  pdf_document:
    toc: no
    highlight: pygments
    includes:
      in_header: header.tex
---




01:940:585:01 - Spring 2024  
Meetings: SPR 319, 10:30--13:20  

Professor: Joseph V. Casillas, PhD  
Email: \href{mailto:joseph.casillas@rutgers.edu}{joseph.casillas@rutgers.edu}  
Office: AB 5174  
Office hours: by appointment


```{r, eval=TRUE, echo=FALSE, cache=FALSE, message=F}
library(RefManageR)
bib <- ReadBib("../bib/span585.bib", check = FALSE)

# Set bib options
BibOptions(bib.style = "authoryear", style = "latex", 
           first.inits = TRUE, check.entries = FALSE)
```






# Part I: Introduction

## Week 1: Overview

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
ui <- "-"
writeLines(ui); print(bib[key = "prieto2014"])
```

### Review

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2010"])
writeLines(ui); print(bib[key = "hualde2014intro"])
writeLines(ui); print(bib[key = "hualde2014consvoc"])
writeLines(ui); print(bib[key = "hualde2014charAcous"])
writeLines(ui); print(bib[key = "campos2012"])
```

<!--
### Programming

- Praat: install, record/save audio
- Github: sign up, install
- R: install
-->








## Week 2: Review, generative and usage-based approaches

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "mccarthy2007"])
writeLines(ui); print(bib[key = "bybee1999"])
```

### Review

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2010"])
writeLines(ui); print(bib[key = "hualde2014intro"])
writeLines(ui); print(bib[key = "hualde2014consvoc"])
writeLines(ui); print(bib[key = "hualde2014charAcous"])
writeLines(ui); print(bib[key = "campos2012"])
```

<!--
### Programming

- Praat: create/save spectrograms I
- Github: Repos 101
-->




## Week 3: Speech perception

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "Diehl2004"])
```

### Review

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "jongman2011ch13"])
```

<!--
### Programming

- Praat: create/save spectrograms II
- Github: forking, commiting, pushing, pulling
-->








## Week 4: L2/Bilingual Speech 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "simonet2012"])
writeLines(ui); print(bib[key = "sls_ch1"])
writeLines(ui); print(bib[key = "sls_ch2"])
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "Best1995"])
writeLines(ui); print(bib[key = "Best:2007ha"])
writeLines(ui); print(bib[key = "Flege:1995wl"])
writeLines(ui); print(bib[key = "VanLeussen2015"])
```

<!--

### Programming

- Praat: All about textgrids

-->







## Week 5: L2/Bilingual Speech

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "flege2001effect"])
writeLines(ui); print(bib[key = "piske2001factors"])
writeLines(ui); print(bib[key = "simonet2019increased"])
```


### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "shea2011experience"])
writeLines(ui); print(bib[key = "rao2015heritage"])
writeLines(ui); print(bib[key = "rao_research_2016"])
```

<!--
### Programming
-->






# Part II: Prosody

## Week 6: Sequences

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "handbook_sp_phon_ch12"])
writeLines(ui); print(bib[key = "sp_pronunciation_ch7"])
writeLines(ui); print(bib[key = "sp_pronunciation_ch8"])
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014enton"])
writeLines(ui); print(bib[key = "jongman2011ch11"])
writeLines(ui); print(bib[key = "Hualde:1989ve"])
writeLines(ui); print(bib[key = "hualde2014silaba"])
writeLines(ui); print(bib[key = "colina2006optimality"])
```




## Week 7: Lexical stress

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "gordon_acoustic_2017"])
writeLines(ui); print(bib[key = "ortega2009perception"])
writeLines(ui); print(bib[key = "kim2019discrepancy"])
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014stress"])
writeLines(ui); print(bib[key = "face_cognitive_2006"])
writeLines(ui); print(bib[key = "OrtegaLlebaria:2011gb"])
```

<!--
### Programming
-->






# Part III: Vocoids

## Week 8: Vocoids I

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "Bradlow:1995wn"])
writeLines(ui); print(bib[key = "hojen2006early"])
writeLines(ui); print(bib[key = "sp_pronunciation_ch1"])
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "jongman2011ch10"])
writeLines(ui); print(bib[key = "hualde2014vocales"])
writeLines(ui); print(bib[key = "Hualde:1997tq"])
```

<!--
### Programming

- R: Grammar of graphics, adv. subsetting, descriptive statistics
- Praat: Loops
-->







## Week 9: Vocoids II

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "Jacewicz:2011kp"])
writeLines(ui); print(bib[key = "pallier1997limit"])
writeLines(ui); print(bib[key = "shea2019dominance"])
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "Bradlow1996"])
writeLines(ui); print(bib[key = "barrios2016similarity"])
writeLines(ui); print(bib[key = "oh2011one"])
```

<!--
### Programming

- R: basic data analysis
- Praat: Formant frequencies, trajectory length
-->







# Part IV: Obstruents

## Week 10: Obstruents I

### Reading


```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "abramson2017voice"])
writeLines(ui); print(bib[key = "Abramson1973"])
writeLines(ui); print(bib[key = "flege1988imitation"])
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014oclusivas"])
writeLines(ui); print(bib[key = "Lisker:1964wl"])
writeLines(ui); print(bib[key = "lisker1967"])
```

<!--
### Programming

- R: Review
- Praat: VOT, Scripts
-->






## Week 11: Obstruents II

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "amengual2012interlingual"])
writeLines(ui); print(bib[key = "Simonet:2012jx"])
writeLines(ui); print(bib[key = "fabiano2015acquisition"])
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "antoniou2011inter"])
writeLines(ui); print(bib[key = "Nadeu:2012ht"])
writeLines(ui); print(bib[key = "simonet2011vx"])
writeLines(ui); print(bib[key = "amengual2017type"])
```

<!--
### Programming

- R: review
- Praat: scripts, spectral moments
-->






## Week 12: Obstruents III

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "torreira2012investigating"])
writeLines(ui); print(bib[key = "ruch2016origin"])
writeLines(ui); print(bib[key = "sp_pronunciation_ch4"])
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "Jongman:2000gr"])
writeLines(ui); print(bib[key = "hualde2014fricAfri"])
writeLines(ui); print(bib[key = "jongman2011ch10"])
writeLines(ui); print(bib[key = "Jongman:2003bf"])
```

<!--
### Programming
-->





# Part V: Sonorants

## Week 13: Nasals, laterals, rhotics

### Reading


```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "sp_pronunciation_ch5"])
writeLines(ui); print(bib[key = "amengual2016acoustic"])
writeLines(ui); print(bib[key = "amengual2018asymmetrical"])
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014nasal"])
writeLines(ui); print(bib[key = "jongman2011ch10"])
writeLines(ui); print(bib[key = "recasens2012cross"])
writeLines(ui); print(bib[key = "henriksen2010acoustic"])
writeLines(ui); print(bib[key = "hualde2014liquids"])
writeLines(ui); print(bib[key = "krakow1993"])
```

<!--
### Programming

- R: residuals
- Praat: formant bandwidth
- Praat: light/dark /l/, trills

-->



























