---
geometry       : vmargin=1.0in, hmargin=0.75in, headsep=0.5in
bibliography   : ../bib/ds4ling_refs.bib
csl            : ../bib/apa.csl
output:
  pdf_document:
    toc: no
    highlight: pygments
    includes:
      in_header: header.tex
---




01:940:658:01 - Spring 2025  
Meetings: Mondays, 10:20--13:20  

Professor: Joseph V. Casillas, PhD  
Email: \href{mailto:joseph.casillas@rutgers.edu}{joseph.casillas@rutgers.edu}  
Office: AB 5174  
Office hours: by appointment

**Note**: Readings must be completed *before* the class that occurs in the assigned week (i.e., readings assigned for week 2 will be discussed *in* the week 2 class, thus they should be read *before*).

```{r}
#| echo: false
#| message: false
#| warnings: false
library("RefManageR")
bib <- ReadBib("../bib/ds4ling_refs.bib", check = FALSE)
```







# Week 2: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
ui <- "-"
writeLines(ui); print(bib["wickham2015"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_preface"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch1"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qml_ch1"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

```

### Additional resources

- [Field Guide to the R Ecosystem (highly recommended)](http://fg2re.sellorm.com)
- [Data science and R: How do I start?](https://medium.com/@kierisi/data-science-and-r-how-do-i-start-7a87426e103e)
- [GitHub for the useR](http://happygitwithr.com)
- [Using Git and GitHub](https://biodatascience.github.io/compbio/github.html)
- [Getting help](https://dcl-2017-04.github.io/curriculum/getting-help.html)











# Week 3: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qml_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch3"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [R for excel users](https://rstudio-conf-2020.github.io/r-for-excel/)
- [RMarkdown cheatsheet](https://posit.co/wp-content/uploads/2022/10/rmarkdown-1.pdf)
- [RMarkdown reference](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf)
- [Getting started with RMarkdown](https://www.rstudio.com/resources/webinars/getting-started-with-r-markdown/)
- [ggplot2 cheatsheet](https://posit.co/wp-content/uploads/2022/10/data-visualization-1.pdf)
- [Secrets to a happy graphing life](http://stat545.com/block016_secrets-happy-graphing.html)
- [A Compendium of Clean Graphs in R](http://shinyapps.org/apps/RGraphCompendium/index.php)









# Week 4: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qml_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch4"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch5"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [The tidyverse style guide](http://style.tidyverse.org)
- [reprex 1](https://dcl-2017-04.github.io/curriculum/reprexes.html)
- [reprex 2](https://github.com/tidyverse/reprex#what-is-a-reprex)
- [Data structure basics](https://dcl-2017-04.github.io/curriculum/data-structure-basics.html)
- [Correlation game](https://gallery.shinyapps.io/correlation_game/)
- [Standardizing and correlations](https://richarddmorey.shinyapps.io/standardizing_and_correlations/)












# Week 5: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass22_ch1"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch6"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch9"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [tidyr tutorial](https://www.jvcasillas.com/tidyr_tutorial/)
- [Tidy data](https://www.jstatsoft.org/article/view/v059i10)
- [Non-tidy data](https://simplystatistics.org/posts/2016-02-17-non-tidy-data/)
- [Creating new variables with mutate and ifelse (advanced)](https://rstudio-pubs-static.s3.amazonaws.com/116317_e6922e81e72e4e3f83995485ce686c14.html#/)












# Week 6: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass57_ch1"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass22_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch8"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch21"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```
- [Slidify tutorial](www.jvcasillas.com/slidify_tutorial/index.html)


### Additional resources

- [Fit-a-line](http://shinyapps.org/showapp.php?app=http://lmpp10e-mucesm.srv.mwn.de:3838/felix/lmfit&by=Felix%20Schönbrodt&title=Find-a-fit!&shorttitle=Find-a-fit!)
- [Simple linear regression game](https://gallery.shinyapps.io/simple_regression/)
- [Bivariate linear regression (shiny)](https://jvcasill.shinyapps.io/shiny_bivariate_regression/)
- [Ordinary least squares regression visualization](https://setosa.io/ev/ordinary-least-squares-regression/)









# Week 7: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass22_ch3"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass57_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```
- [xaringan tutorial 1](https://slides.yihui.name/xaringan/#1)
- [xaringan tutorial 2](http://www.jvcasillas.com/ru_xaringan/slides/index.html#1)



### Additional resources

- [R Markdown presentations](https://dcl-2017-04.github.io/curriculum/rmarkdown-formats.html)
- [Model choices/interactions](https://gallery.shinyapps.io/multi_regression/)
- [Diagnostics for simple linear regression](https://gallery.shinyapps.io/slr_diag/)








# Spring break (highly recommended walk through): 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["r4ds_ch18"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch19"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

Corresponds with chapters [22][22], [23][23], [24][24], and [25][25] online. 

[22]: http://r4ds.had.co.nz/model-intro.html
[23]: https://r4ds.had.co.nz/model-basics.html
[24]: https://r4ds.had.co.nz/model-building.html
[25]: https://r4ds.had.co.nz/many-models.html






# Week 8: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass57_ch5"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass50_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass50_ch4"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```
- [papaja documentation](https://frederikaust.com/papaja_man/): Read documentation, 
install package and play with demo example.


### Additional resources

- [Multicollinearity](https://gallery.shinyapps.io/collinearity/)
- [More papaja](https://rpubs.com/YaRrr/papaja_guide)
- [R Markdown with papaja (video pt. 1)](https://www.youtube.com/watch?v=I_HW5Rraqg8)
- [R Markdown with papaja (video pt. 2)](https://www.youtube.com/watch?v=dmB6sHDbs7Q)









# Week 9: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass93_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass93_ch3"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass93_ch4"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [Model choices/interactions](https://gallery.shinyapps.io/multi_regression/)
- [StackOverflow question w/ good answer](https://stats.stackexchange.com/questions/94010/understanding-dummy-manual-or-automated-variable-creation-in-glm)
- [Dummy variables (video)](https://www.youtube.com/watch?v=2s8AwoKZ-UE)







# Week 10: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass93_ch5"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [Coding systems](https://stats.idre.ucla.edu/r/library/r-library-contrast-coding-systems-for-categorical-variables/)
- [Coding schemes for categorical variables in regression](http://www.mypolyuweb.hk/~sjpolit/coding_schemes.html)






# Week 11: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["stat_rethink_ch9"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

writeLines(ui); print(bib["gelman_hill_ch5"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

writeLines(ui); print(bib["gelman_hill_ch6"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [Generalised Linear Models in R](https://magesblog.com/post/2015-08-04-generalised-linear-models-in-r/)
- [Shiny GLM](https://jvcasill.shinyapps.io/shiny_glm/)
- [When to use logistic regression](http://logisticregressionanalysis.com/33-when-to-use-logistic-regression/)
- [Why regular regression does NOT work](http://logisticregressionanalysis.com/55-why-regular-regression-does-not-work/)
- [What is (multivariate) logistic regression](http://logisticregressionanalysis.com/86-what-is-logistic-regression/)













# Week 12: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["brown2021"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [DeBruine & Barr (2021)](https://journals.sagepub.com/doi/10.1177/2515245920965119)
- https://shiny.psy.gla.ac.uk/lmem_sim/
- http://mfviz.com/hierarchical-models/




# Week 13: 

### Reading

- [Bayesian thinking for toddlers](https://psyarxiv.com/w5vbp/)
- [Seeing theory: Frequentist inference](https://seeing-theory.brown.edu/index.html#secondPage/chapter4)
- [Seeing theory: Bayesian inference](https://seeing-theory.brown.edu/index.html#secondPage/chapter5)
- [Basic Bayesian analysis](https://m-clark.github.io/easy-bayes/basic-bayesian-analysis.html)

### Additional reading

- [Interactive visualization](https://rpsychologist.com/d3/bayes/)
- https://www.tjmahr.com/bayesplot-satrdays-2019/#/



# Readings to keep you occupied after S2025 

### Reading

- [Common statistical tests are linear models](https://lindeloev.github.io/tests-as-linear/)
- [Bayesian statistics with R](https://oliviergimenez.github.io/bayesian-stats-with-R/)
- [An introduction to Bayesian Data Analysis for Cognitive Science](https://vasishth.github.io/bayescogsci/)




