---
title        :
author       : ""
date         : ""
fontsize     : 10pt
geometry     : vmargin=1in, hmargin=1in, headsep=.5in
bibliography : refs/bib/ldius.bib
csl          : refs/bib/apa.csl
output:
  pdf_document:
    toc: no
    highlight: pygments
    includes:
      in_header: header.tex
    latex_engine: xelatex
---


\normalsize

01:090:293:01 - Spring 2023  
Meetings: HC S120, 10:20--13:20  
Professor: Joseph V. Casillas, PhD  
Email: \href{mailto:joseph.casillas@rutgers.edu}{joseph.casillas@rutgers.edu}  
Office: AB 5174  
Office hours: by appointment

# Course description

All languages show variation over time and space. 
From the moment we are exposed to our first language, we begin to take note of *who* says *what* and *how* they say it. 
A fundamental tenet of our nation is that discrimination on the grounds of skin color, ethnicity, gender, or age is unacceptable.
Yet, it seems we do not apply this same principle to language. 
On the contrary, it is commonplace for individuals and groups of people to be judged on the basis of language form rather than language content. 
This course focuses on language, ideology, and linguistic discrimination, with a focus on the context of the United States. 
We will examine our beliefs about the nature of language and its use in the social world (language ideologies), as well as consider situations in which a given language or language variety is ascribed hegemonic power over others (language subordination). 
Students will learn a model of language subordination and come to understand how it both contributes to and results from policy, planning, and education. 
We will focus on principles of language variation and change that will show that language subordination and discrimination are equivalent to other forms of discrimination. 
Through case studies and personal reflection, students will critically analyze myths about accents and standard language ideologies---both their own and those of others---with the primary goal of becoming linguist(ic) activists.  
**Prerequisites**: None.


# Materials

### Class websites

- Canvas: https://rutgers.instructure.com/courses/211354

### Books

```{r, bib-setup, eval=TRUE, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
library(RefManageR)
bib <- ReadBib("./refs/bib/ldius.bib", check = FALSE)
ui <- "- "
```

```{r, print-bib, results='asis', echo=FALSE, eval=TRUE, cache=FALSE, warning=FALSE, message=FALSE}
writeLines(ui)
print(bib[key = "lippi2012english"], 
  .opts = list(check.entries = FALSE, 
               style = "latex", 
               bib.style = "authoryear"))
```


### Weekly readings

Students are assigned weekly readings to be completed before class meets.
All readings will be available in electronic format (.pdf) via canvas.


# Coursework

### Evaluation

\begin{center}
\begin{tabular}{lrp{0.75in}lr}
\toprule
Component                     & Percentage & & \multicolumn{2}{c}{Grade distribution} \\
\cmidrule(lr){1-2}
\cmidrule(lr){4-5}
Preparation and participation & 15\%       & & A  & 92--100 \\
Online discussion             & 15\%       & & B+ & 87--91  \\
Personal reflections          & 20\%       & & B  & 80--86  \\
Reading responses             & 15\%       & & C+ & 77--79  \\
Discrimination in the wild    & 15\%       & & C  & 70--76  \\
Research project              & 20\%       & & D  & 65--69  \\
 - Group presentation (10\%)  &            & & F  &  0--64  \\
 - Paper (10\%)               &            & &    &         \\
\bottomrule
\end{tabular}
\end{center}

### Preparation and participation

Students are expected to attend class prepared and to actively participate. 

### Online discussion

Occasionally students will be asked to respond to prompts and/or discuss readings using the canvas discussion forum. 
Posts should be respectful, relevant contributions to the topic at hand and should be submitted *before* coming to class. 

### Personal reflections

In these exercises students will be given a prompt and asked to reflect on their own attitudes toward non‐standard language or accents; some also require gathering information from other people and comparing their responses. (approx. 1 page)

### Reading responses

Similar to online discussions, occasionally students will be asked to discuss a particular reading. 
Reading responses differ from online discussions in that they are expected to be longer (approx. 1 page) and more formal. 
Reading responses should be microsoft word documents submitted via canvas. 

### Discrimination in the wild

Students will find and document examples of linguistic prejudice in the wild. 
These can be video/audio clips, articles from written media (newspapers, blogs), or a narrative video describing a personal experience. 
Examples should be posted to the discussion board on Canvas and be accompanied by a short (50‐100 words) statement of how the example illustrates linguistic prejudice as discussed in the course.

### Research Project

\textcolor{RUred}{Group presentation}:
In groups of 2‐3, students will identify a set of speakers targeted by linguistic prejudice and some documented negative outcome of linguistic discrimination and propose steps towards mitigation. 
Students can propose their own topics/groups, but they should shoud be approved by the professor. 
There will be in‐class prep time and group presentations (15‐20 minutes) will take place in the final weeks of the semester.

\textcolor{RUred}{Paper}:
Each student will individually write up an expanded version of their group project providing (a) the background on a documented prejudice and/or discrimination towards some set of speakers (b) a proposal for reduction of prejudice or mitigation of its discriminatory effects and (c) a discussion of the relationship of the proposal to other proposals for mitigations and their ethical bases (5‐8 pages).

# Department rules and course policy

The course is designed to satisfy the learning goals of the Department of Spanish and Portuguese. 
More information available at: http://span-port.rutgers.edu/learning-goals


### Communication

All course communication will be via email. 
Remember that all correspondence should include your name, RU id, and the course title/number. 


### Attendance

Regular class attendance is essential for successful completion of the course. 
More than 1 absences will have a negative effect on your final grade. 
The 2nd absence and every subsequent absence after that will result in the loss of 5\% point off the final overall course grade, regardless of reason. 
Keep in mind that while you have 1 "free" absence, on the day/s you miss you will not be able to earn participation points, you will miss the material given in class and you might miss your own presentation. 
If you are absent, contact a classmate immediately to get the assignments and to keep up with the material scheduled in the syllabus. 
The instructor is not responsible for catching you up. 
Do not send emails to the instructor asking for updates if you missed class.

Any planned absence that you are aware of ahead of time, such as religious  holidays recognized by Rutgers University or Dean's excuses, should be  made up before the absence occurs. 
If you know that you will be absent, it is your responsibility to let the instructor know ahead of time. 
All holidays or special events observed by any religion will be honored for those students who show affiliation with that particular religion. 
Absences pre-approved by the RU Dean of Students (or Dean's designee) will be honored.


### Code of academic integrity

The professor will initiate an academic integrity case against students suspected of cheating, plagiarizing, or aiding others in dishonest academic behavior. 
Students are responsible for reading and understanding the Code of Academic Integrity.

Examples of academic dishonesty include, but are not limited to, plagiarism,  cheating, and aiding and abetting dishonesty. 
An example of plagiarism would be to submit a written sample which in part or in whole is not the student's own work without attributing the source. 
Cheating includes allowing another person to do your work and to submit the work under one's own name. 
Any work which is submitted for a grade must be 100% the student's own work. 
If you are not sure when it is appropriate to seek help, please see the professor.

\vspace{0.2in}
\hrule  
\textcolor{RUred}{Plagiarism} is the use of another person’s words, ideas, or results without giving that person appropriate credit. 
Do not plagiarize.

\scriptsize{Rutgers University Academic Integrity Policy, p. 2: http://academicintegrity.rutgers.edu/files/documents/AI\_Policy\_2013.pdf}
\vspace{.1in}
\hrule

\vspace{0.3in}
\normalsize

For more information 

- http://academicintegrity.rutgers.edu/ 
- http://www.libraries.rutgers.edu/avoid_plagiarism. 


### Students with disabilities

Rutgers University welcomes students with disabilities into all of the  University's educational programs. 
In order to receive consideration for reasonable accommodations, a student with a disability must contact the appropriate disability services office at the campus where you are officially enrolled, participate in an intake interview, and provide documentation:  
[https://ods.rutgers.edu/students/documentation-guidelines](https://ods.rutgers.edu/students/documentation-guidelines).  

If the documentation supports your request for reasonable accommodations, your  campus's disability services office will provide you with a Letter of
Accommodations. 
Please share this letter with your instructors and discuss the accommodations with them as early in your courses as possible. 
To begin this process, please complete the Registration form on the ODS web site at: [https://ods.rutgers.edu/students/registration-form](https://ods.rutgers.edu/students/registration-form).

\clearpage

## Tentative schedule (subject to change)

\renewcommand{\arraystretch}{1}

```{r, syllabus-293, child="./calendar/calendar_s2023.Rmd"}
```
