---
geometry       : vmargin=1.0in, hmargin=0.75in
bibliography   : ../bib/span585.bib
csl            : ../bib/apa.csl
output:
  pdf_document:
    toc: no
    highlight: pygments
    includes:
      in_header: header.tex
---




01:940:585:01 - Spring 2017  
Meetings: AB 5190, 09:50--12:50  

Professor: Joseph V. Casillas, PhD  
Email: \href{mailto:joseph.casillas@rutgers.edu}{joseph.casillas@rutgers.edu}  
Office: AB 5174  
Office hours: by appointment


```{r, eval=TRUE, echo=FALSE, cache=FALSE}
library(RefManageR)
bib <- ReadBib("../bib/span585.bib", check = FALSE)
```






# Part I: Introduction

## Week 1: Overview

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
ui <- "-"
uiP <- "- \\*"
writeLines(ui); print(bib[key = "prieto2014"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Review

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2010"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014intro"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014consvoc"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014charAcous"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "campos2012"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: install, simple math, install/load packages, data structures, RMarkdown
- Praat: install, record/save audio










## Week 2: Review, generative approaches

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "mccarthy2007"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "bybee1999"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Review

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2010"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014intro"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014consvoc"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014charAcous"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "campos2012"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: data structures, vectorized math, subsetting
- Praat: create/save spectrograms I






## Week 3: Review, generative and usage-based approaches

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "mccarthy2007"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "bybee1999"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Review

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2010"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014intro"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014consvoc"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014charAcous"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "campos2012"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: getting/loading data, tidy data, simple visualization
- Praat: create/save spectrograms II









# Part II: Production

## Week 4: Sequences

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "Hualde:1989ve"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Extra

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014silaba"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "colina2006optimality"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: Data manipulation, subsetting, grammar of graphics
- Praat: All about textgrids











## Week 5: Vocoids I

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(uiP); print(bib[key = "Bradlow:1995wn"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "jongman2011ch10"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014vocales"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "Hualde:1997tq"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: Grammar of graphics, adv. subsetting, descriptive statistics
- Praat: Loops








## Week 6: Vocoids II

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(uiP); print(bib[key = "Escudero:2009ue"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "willis2005initial"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "Jacewicz:2011kp"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: basic data analysis
- Praat: Formant frequencies, trajectory length







## Week 7: Obstruents I

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(uiP); print(bib[key = "Lisker:1964wl"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014oclusivas"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "lisker1967"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "Simonet:2012jx"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: Review
- Praat: VOT, Scripts








## Week 8: Obstruents II

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(uiP); print(bib[key = "Jongman:2000gr"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014fricAfri"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "jongman2011ch10"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "Nadeu:2012ht"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "simonet2011vx"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: review
- Praat: scripts, spectral moments







## Week 9: Sonorants I

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(uiP); print(bib[key = "krakow1993"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014nasal"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "jongman2011ch10"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: residuals
- Praat: formant bandwidth






## Week 10: Sonorants II


### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(uiP); print(bib[key = "recasens2012cross"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(uiP); print(bib[key = "henriksen2010acoustic"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

## Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014liquids"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "jongman2011ch10"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: residuals
- Praat: light/dark /l/, trills







## Week 11: Prosody: lexical stress, rhythm, entonation

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "OrtegaLlebaria:2011gb"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(uiP); print(bib[key = "Prieto:2007tw"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "hualde2014stress"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "hualde2014enton"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "jongman2011ch11"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: 
- Praat: peak alignment, low-pass filtering











\clearpage

# Part III: Perception

## Week 12: Perception theory

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "Diehl2004"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(uiP); print(bib[key = "Abramson1973"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "jongman2011ch13"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- Psychopy: sitmuli presentation, project management







## Week 13: Categorical perception

### Reading


```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(uiP); print(bib[key = "Bradlow1996"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "Jongman:2003bf"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Recommended

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib[key = "jongman2011ch13"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

- R: analyzing perceptual data
- Psychopy: stimuli presentation







