---
geometry       : vmargin=1.0in, hmargin=0.75in, headsep=0.5in
bibliography   : ../bib/ldius.bib
csl            : ../bib/apa.csl
output:
  pdf_document:
    toc: no
    highlight: pygments
    includes:
      in_header: header.tex
---

01:940:293:01 - Spring 2023  
Meetings: Fridays, 10:20--13:20  

Professor: Joseph V. Casillas, PhD  
Email: \href{mailto:joseph.casillas@rutgers.edu}{joseph.casillas@rutgers.edu}  
Office: AB 5174  
Office hours: by appointment

**Note**: Readings must be completed *before* the class that occurs 
in the assigned week (i.e., readings assigned for week 2 will be 
discussed *in* the week 2 class, thus they should be read *before*.).

```{r}
#| label: load-refs
#| echo: false
#| message: false
library("RefManageR")
library("here")
bib <- ReadBib(here("293", "refs", "bib", "ldius.bib"), check = FALSE)
```

# Week 2: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
ui <- "-"
writeLines(ui); print(bib["ewa_intro"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["ewa_ch1"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

```

# Week 3: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch3"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

writeLines(ui); print(bib["ewa_ch4"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```


# Week 4: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch6"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

writeLines(ui); print(bib["ewa_ch7"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

# Week 5: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["strangor_2009"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["becker_2018"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["kibler_2018"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["clopper_2018"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

# Week 6: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch10"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["smedley2005race"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

```

# Week 7: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch10"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["ewa_ch14"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

```

# Week 8: (no in class meeting)

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch10"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

# Week 9: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch11"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

# Week 10: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch13"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["rubin1990effects"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

# Week 11: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ko2009stereotyping"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["campbell2007accent"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

```

# Week 12: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch9"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["anderson2014vocal"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```


# Week 13: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch17"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

writeLines(ui); print(bib["purnell1999perceptual"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

# Week 14: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["ewa_ch18"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

writeLines(ui); print(bib["wolfram2013sound"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

```
- HR Daily Advisor. 2016. “Avoiding Language Discrimination in the Workplace”:
https://hrdailyadvisor.blr.com/2016/03/14/avoiding-language-discrimination-in-the- workplace/

