---
geometry       : vmargin=1.0in, hmargin=0.75in
bibliography   : refs/bib/span585.bib
csl            : refs/bib/apa.csl
output:
  pdf_document:
    toc: no
    highlight: pygments
    includes:
      in_header: header.tex
---




01:940:585:01 - Spring 2020  
Meetings: AB 5190, 08:10--11:10  

Professor: Joseph V. Casillas, PhD  
Email: \href{mailto:joseph.casillas@rutgers.edu}{joseph.casillas@rutgers.edu}  
Office: AB 5174  
Office hours: by appointment



# Course description

This course serves as an introduction to Spanish phonetics and phonology. 
As such, a principle aim is to provide a general descriptive vision of the 
Spanish phonological system. 
This course will examine various analyses provided by phonological and 
phonetic research. 
To this end, this course will provide an introduction to formal generative 
accounts of Spanish phonology (both serial and parallel models), as well as 
usage-based accounts.
The sounds of Spanish will also be approached from the perspective of 
experimental, instrumental, quantitative phonetics. 
An important objective of this course is to help students acquire the 
fundamental skills necessary in order to carry out experimental speech 
research. 
This includes issues such as hypothesis testing, experimental design, 
quantitative data collection and archiving, quantitative analysis and, 
finally, interpretation of the implications of experimental results. 
Students will learn to use fundamental tools such as Praat (digital speech 
processing) and R (statistics, graphics).

# Materials

## Class websites

- https://rutgers.instructure.com/courses/46204
- Presentations and scripts here: www.jvcasillas.com/  

## Recommended books

```{r, eval=TRUE, echo=FALSE, cache=FALSE}
library(RefManageR)
bib <- ReadBib("./refs/bib/span585.bib", check = FALSE)
```

### Phonetics/Phonology

```{r, results='asis', echo=FALSE, eval=TRUE, cache=FALSE}
ui <- "-"
writeLines(ui); print(bib[key = "sonidosDelEsp2014"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "cedeno2014fonologia"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "phoneticsJongman2011"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

\vspace{.1in}

```{r, results='asis', echo=FALSE, eval=TRUE, cache=FALSE}
writeLines(ui); print(bib[key = "handbookHispLing2012"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "introLingHisp2010"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

```{r, results='asis', echo=FALSE, eval=TRUE, cache=FALSE}
writeLines(ui); print(bib[key = "r4datascience2017"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "ggplot22016"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "xie2015dynamic"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

## Weekly readings

Students will receive a package of additional readings to be distributed in 
electronic format (.pdf).

Main journals: 

- Journal of Phonetics
- Phonetica
- Journal of the Acoustical Society of America 
- Journal of the International Phonetic Association
- Language & Speech
- Cognition




# Coursework

## Evaluation

\begin{center}
\begin{tabular}{lrp{0.75in}lr}
\toprule
Component                     & Percentage & & \multicolumn{2}{c}{Grade distribution} \\
\cmidrule(lr){1-2}
\cmidrule(lr){4-5}
Preparation and participation & 10\%       & & A  & 92--100 \\
Programming assignments       & 40\%       & & B+ & 87--91 \\
Presentations                 & 25\%       & & B  & 80--86 \\
Final paper                   & 25\%       & & C+ & 77--79 \\
                              &            & & C  & 70--76 \\
                              &            & & D  & 65--69 \\
                              &            & & F  & 0--64 \\
\bottomrule
\end{tabular}
\end{center}

## Summaries and presentations

Students will write a brief summary (max. 1 page) of each reading (excluding 
chapters). 
Summaries will be handed in via canvas dropbox the day before class meets, 
before 10pm.

After the fourth week of class, students will begin to lead discussion for 
the readings assigned during the remainder of the course. 
Presentation order and assignments will be established during the first weeks 
of class. 
The student responsible for leading discussion should prepare slides, a 
handout, and questions/ideas to foment participation among peers.

## Programming assignments

Throughout the semester we will have workshops in class covering important 
programming topics in Praat and R. 
The workshops aim to help students develop skills that are relevant to 
scientific research in general and speech research more specifically.

Students will complete 4 programming assignments over the course of the 
semester. 
These assignments are designed in a way so that the student must demonstrate 
adequate knowledge of basic programming principles covered in class workshops. 
The skills required in each assignment are cumulative, each building on the 
material learned in the previous weeks.

## Project

Each student will complete a research project. 
There are four options:

1. Research paper ([ICPhS](http://www.icphs2015.info/Call.aspx) format)
	- for advanced students w/ data
	- goal: presentation at regional conference
2. Pilot study ([ICPhS](http://www.icphs2015.info/Call.aspx) format)
  - for new/advanced students with ideas, but no data
  - conduct study (propose, design, data collection/analysis, write up), 
  collaboration ok
  - goal: (a) conference presentation/journal submission (w/ IRB), (b) 
  complete groundwork for future project (w/o IRB)
3. Research proposal ([ICPhS](http://www.icphs2015.info/Call.aspx) format w/ 
fake data, or publicaly available dataset)
	- for new/advanced students with ideas, but no data
	- focus on lit review, design, programming/stats
	- goal: complete groundwork for future project
4. Phonetic/phonological issue summary (APA format, 15-20 pages)
	- for new/unsure student, no ideas, no data
	- goal: demonstrate expertise in theoretical issue regarding Spanish 
	phonetics/phonology
	- Ex: phonological paper detailing spirantization in serial/parallel models 
	in generative phonology

All projects require the prior approval of the professor. 
Projects are due on the day and time of the university assigned final exam 
(though there is no exam). 
Students will present their work in a semi-finished state during the final two 
weeks of the semester (20 min. presentation + 10 min. for questions).



# Department rules and course policy

### Attendance

Regular class attendance is essential for successful completion of the course. 
More than 1 absences will have a negative effect on your final grade. The 2nd 
absence and every subsequent absence after that will result in the loss of 5\% 
point off the final overall course grade, regardless of reason. Keep in mind 
that while you have 1 "free" absence, on the day/s you miss you will not be able 
to earn participation points, you will miss the material given in class and you 
might miss your own presentation. If you are absent, contact a classmate 
immediately to get the assignments and to keep up with the material scheduled in 
the syllabus. The instructor is not responsible to put you up to date. Do not 
send emails to the instructor asking for updates if you missed class.

Any planned absence that you are aware of ahead of time, such as religious 
holidays recognized by Rutgers University or Dean's excuses, should be 
made up before the absence occurs. If you know that you will be absent, it is 
your responsibility to let the instructor know ahead of time. All holidays or 
special events observed by any religion will be honored for those students who 
show affiliation with that particular religion. Absences pre-approved by the RU 
Dean of Students (or Dean's designee) will be honored.

### Code of academic integrity

The professor will initiate an academic integrity case against students 
suspected of cheating, plagiarizing, or aiding others in dishonest academic 
behavior. Students are responsible for reading and understanding the Code of 
Academic Integrity.

Examples of academic dishonesty include, but are not limited to, plagiarism, 
cheating, and aiding and abetting dishonesty. An example of plagiarism would be 
to submit a written sample which in part or in whole is not the student's own 
work without attributing the source. Cheating includes allowing another person 
to do your work and to submit the work under one's own name. Any work which is 
submitted for a grade must be 100% the student's own work. If you are not sure 
when it is appropriate to seek help, please see the professor.


\vspace{0.2in}
\hrule  
\textcolor{RUred}{Plagiarism} is the use of another person’s words, ideas, or 
results without giving that person appropriate credit. Do not plagiarize.

\scriptsize{Rutgers University Academic Integrity Policy, p. 2: http://academicintegrity.rutgers.edu/files/documents/AI\_Policy\_2013.pdf}
\vspace{.1in}
\hrule

\vspace{0.3in}
\normalsize

For more information 

- http://academicintegrity.rutgers.edu/ 
- http://www.libraries.rutgers.edu/avoid_plagiarism. 


### Students with disabilities

Rutgers University welcomes students with disabilities into all of the 
University's educational programs. In order to receive consideration for 
reasonable accommodations, a student with a disability must contact the 
appropriate disability services office at the campus where you are officially 
enrolled, participate in an intake interview, and provide documentation: 
[https://ods.rutgers.edu/students/documentation-guidelines](https://ods.rutgers.edu/students/documentation-guidelines).  

If the documentation supports your request for reasonable accommodations, your 
campus’s disability services office will provide you with a Letter of 
Accommodations. Please share this letter with your instructors and discuss the 
accommodations with them as early in your courses as possible. To begin this 
process, please complete the Registration form on the ODS web site at: 
[https://ods.rutgers.edu/students/registration-form](https://ods.rutgers.edu/students/registration-form).
















\vspace{.2in}

|               | Week |  Date |                           Topic                            |
| :------------ | :--: | :---: | :--------------------------------------------------------- |
|               |      |       |                                                            |
| **Part I:**   |      |       |                                                            |
| Introduction  |      |       |                                                            |
|               |  1   | 01/23 | Overview of Spanish phonology                              |
|               |  2   | 01/30 | Overview (cont.), generative approaches                    |
|               |  3   | 02/06 | Speech perception                                          |
|               |  4   | 02/13 | L2/Bilingual Speech, PA1                                   |
|               |  5   | 02/20 | L2/Bilingual Speech (cont.)                                |
| **Part II:**  |      |       |                                                            |
| Prosody       |      |       |                                                            |
|               |  6   | 02/27 | Prosody I: Sequences                                       |
|               |  7   | 03/05 | Prosody II: Lexical stress, PA2                            |
| **Part III:** |      |       |                                                            |
| Vocoids       |      |       |                                                            |
|               |  8   | 03/12 | Vocoids I                                                  |
|               |      | 03/19 | **Spring break**                                           |
|               |  9   | 03/26 | Vocoids II, PA3                                            |
| **Part IV:**  |      |       |                                                            |
| Obstruents    |      |       |                                                            |
|               |  10  | 04/02 | Obstruents I: Stops                                        |
|               |  11  | 04/09 | Obstruents II: Stops, PA4                                  |
|               |  12  | 04/16 | Obstruents III: Fricatives/affricates                      |
| **Part V:**   |      |       |                                                            |
| Sonorants     |      |       |                                                            |
|               |  13  | 04/23 | Sonorants: Nasals, laterals and rhotics                    |
|               |      |       |                                                            |
|               |  14  | 04/30 | Presentations, residuals                                   |
|               |  15  | 05/?? | Reading day                                                |
|               |  16  | 05/?? | Final exam day (presentations if necessary)                |
