---
geometry       : vmargin=1.0in, hmargin=0.75in
bibliography   : refs/bib/span650.bib
csl            : refs/bib/apa.csl
output:
  pdf_document:
    toc: no
    highlight: pygments
    includes:
      in_header: header.tex
---


\begin{wrapfigure}[1]{r}{0.21\textwidth}
\includegraphics[width=0.2\textwidth]{intro_phonetics_grad.png}
\end{wrapfigure}

01:940:650:01 - Spring 2022  
Meetings: AB 5190, Monday, 10:20--13:20  

Professor: Joseph V. Casillas, PhD  
Email: \href{mailto:joseph.casillas@rutgers.edu}{joseph.casillas@rutgers.edu}  
Office: AB 5174  
Office hours: by appointment



# Course description

This course serves as an introduction to Spanish phonetics and phonology. 
As such, a principle aim is to provide a general descriptive vision of the Spanish phonological system. 
This course will examine various analyses provided by phonological and phonetic research. 
To this end, this course will provide an introduction to formal generative accounts of Spanish phonology (both serial and parallel models), as well as usage-based accounts. 
The sounds of Spanish will also be approached from the perspective of experimental, instrumental, quantitative phonetics. 
An important objective of this course is to help students acquire the fundamental skills necessary in order to carry out experimental speech research. 
This includes issues such as hypothesis testing, experimental design, quantitative data collection and archiving, quantitative analysis and, finally, interpretation of the implications of experimental results. 
Students will learn to use fundamental tools such as Praat (digital speech processing) and R (statistics, graphics).

# Materials

## Class websites

- Canvas: https://rutgers.instructure.com/courses/169347

## Recommended books

```{r, eval=TRUE, echo=FALSE, cache=FALSE, message=F}
library(RefManageR)
bib <- ReadBib("./refs/bib/span650.bib", check = FALSE)
```

### Phonetics/Phonology

```{r, results='asis', echo=FALSE, eval=TRUE, cache=FALSE}
ui <- "-"
writeLines(ui); print(bib[key = "sonidosDelEsp2014"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "cedeno2014fonologia"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "phoneticsJongman2011"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

```{r, results='asis', echo=FALSE, eval=TRUE, cache=FALSE}
writeLines(ui); print(bib[key = "handbookHispLing2012"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "introLingHisp2010"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

### Programming

```{r, results='asis', echo=FALSE, eval=TRUE, cache=FALSE}
writeLines(ui); print(bib[key = "r4datascience2017"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "ggplot22016"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
writeLines(ui); print(bib[key = "xie2015dynamic"], .opts = list(check.entries = FALSE, 
                      style = "latex", bib.style = "authoryear"))
```

\clearpage
\phantom{.}
\vspace{0.2in}

## Weekly readings

Students will receive a package of additional readings to be distributed in electronic format (.pdf).

Main journals: 

- Journal of Phonetics
- Phonetica
- Journal of the Acoustical Society of America 
- Journal of the International Phonetic Association
- Language & Speech
- Cognition




# Coursework

## Evaluation

\begin{center}
\begin{tabular}{lrp{0.75in}lr}
\toprule
Component                     & Percentage & & \multicolumn{2}{c}{Grade distribution} \\
\cmidrule(lr){1-2}
\cmidrule(lr){4-5}
Preparation and participation & 10\%       & & A  & 92--100 \\
Programming assignments       & 40\%       & & B+ & 87--91 \\
Presentations                 & 25\%       & & B  & 80--86 \\
Final paper                   & 25\%       & & C+ & 77--79 \\
                              &            & & C  & 70--76 \\
                              &            & & D  & 65--69 \\
                              &            & & F  & 0--64 \\
\bottomrule
\end{tabular}
\end{center}

## Summaries and presentations

Students will write a brief summary (max. 1 page) of each reading (excluding chapters). 
Summaries will be handed in via canvas dropbox the day before class meets, before 10pm.

After the fourth week of class, students will begin to lead discussion for the readings assigned during the remainder of the course. 
Presentation order and assignments will be established during the first weeks of class. 
The student responsible for leading discussion should prepare slides, a handout, and questions/ideas to foment participation among peers.

## Programming assignments

Throughout the semester we will have workshops in class covering important programming topics in Praat and R. 
The workshops aim to help students develop skills that are relevant to scientific research in general and speech research more specifically.

Students will complete 4 programming assignments over the course of the semester. 
These assignments are designed in a way so that the student must demonstrate adequate knowledge of basic programming principles covered in class workshops. 
The skills required in each assignment are cumulative, each building on the material learned in the previous weeks.


\clearpage
\phantom{.}
\vspace{0.2in}


## Project

Each student will complete a research project. 
There are four options:

1. Research paper ([ICPhS](http://www.icphs2015.info/Call.aspx) format)
    - for advanced students w/ data
    - goal: presentation at regional conference
2. Pilot study ([ICPhS](http://www.icphs2015.info/Call.aspx) format)
    - for new/advanced students with ideas, but no data
    - conduct study (propose, design, data collection/analysis, write up), collaboration ok
    - goal: (a) conference presentation/journal submission (w/ IRB), (b) complete groundwork for future project (w/o IRB)
3. Research proposal ([ICPhS](http://www.icphs2015.info/Call.aspx) format w/ 
fake data, or publicaly available dataset)
    - for new/advanced students with ideas, but no data
    - focus on lit review, design, programming/stats
    - goal: complete groundwork for future project
4. Phonetic/phonological issue summary (APA format, 15-20 pages)
    - for new/unsure student, no ideas, no data
    - goal: demonstrate expertise in theoretical issue regarding Spanish phonetics/phonology
    - Ex: phonological paper detailing spirantization in serial/parallel models in generative phonology

All projects require the prior approval of the professor. 
Projects are due on the day and time of the university assigned final exam (though there is no exam). 
Students will present their work in a semi-finished state during the final two weeks of the semester (20 min. presentation + 10 min. for questions).



# Department rules and course policy

### Attendance

Regular class attendance is essential for successful completion of the course.  
More than 1 absences will have a negative effect on your final grade. 
The 2nd absence and every subsequent absence after that will result in the loss of 5\% point off the final overall course grade, regardless of reason. 
Keep in mind that while you have 1 "free" absence, on the day/s you miss you will not be able to earn participation points, you will miss the material given in class and you might miss your own presentation. 
If you are absent, contact a classmate immediately to get the assignments and to keep up with the material scheduled in the syllabus. 
The instructor is not responsible to put you up to date. 
Do not send emails to the instructor asking for updates if you missed class. 

Any planned absence that you are aware of ahead of time, such as religious holidays recognized by Rutgers University or Dean's excuses, should be made up before the absence occurs. 
If you know that you will be absent, it is your responsibility to let the instructor know ahead of time. All holidays or special events observed by any religion will be honored for those students who show affiliation with that particular religion. 
Absences pre-approved by the RU Dean of Students (or Dean's designee) will be honored.


\clearpage
\phantom{.}
\vspace{0.2in}

### Code of academic integrity

The professor will initiate an academic integrity case against students suspected of cheating, plagiarizing, or aiding others in dishonest academic behavior. 
Students are responsible for reading and understanding the Code of Academic Integrity.

Examples of academic dishonesty include, but are not limited to, plagiarism, cheating, and aiding and abetting dishonesty. 
An example of plagiarism would be to submit a written sample which in part or in whole is not the student's own work without attributing the source. 
Cheating includes allowing another person to do your work and to submit the work under one's own name. 
Any work which is submitted for a grade must be 100% the student's own work. 
If you are not sure when it is appropriate to seek help, please see the professor.

\vspace{0.2in}
\hrule  
\textcolor{RUred}{Plagiarism} is the use of another person's words, ideas, or results without giving that person appropriate credit. 
Do not plagiarize.

\scriptsize{Rutgers University Academic Integrity Policy, p. 2: http://academicintegrity.rutgers.edu/files/documents/AI\_Policy\_2013.pdf}
\vspace{.1in}
\hrule

\vspace{0.3in}
\normalsize

For more information 

- http://academicintegrity.rutgers.edu/ 
- http://www.libraries.rutgers.edu/avoid_plagiarism. 


### Students with disabilities

Rutgers University welcomes students with disabilities into all of the  University's educational programs. 
In order to receive consideration for reasonable accommodations, a student with a disability must contact the appropriate disability services office at the campus where you are officially enrolled, participate in an intake interview, and provide documentation:  [https://ods.rutgers.edu/students/documentation-guidelines](https://ods.rutgers.edu/students/documentation-guidelines).

If the documentation supports your request for reasonable accommodations, your  campus's disability services office will provide you with a Letter of Accommodations. 
Please share this letter with your instructors and discuss the accommodations with them as early in your courses as possible. 
To begin this process, please complete the Registration form on the ODS web site at:  
[https://ods.rutgers.edu/students/registration-form](https://ods.rutgers.edu/students/registration-form).

\clearpage
\phantom{.}
\vspace{1.2in}

```{r, cal-585, child="./calendar/calendar_s2022.Rmd"}
```
