---
geometry       : vmargin=1.0in, hmargin=0.75in
bibliography   : ../bib/span589.bib
csl            : ../bib/apa.csl
output:
  pdf_document:
    toc: no
    highlight: pygments
    includes:
      in_header: header.tex
---




01:940:589:01 - Spring 2021  
Meetings: via Zoom, 08:10--11:10  

Professor: Joseph V. Casillas, PhD  
Email: \href{mailto:joseph.casillas@rutgers.edu}{joseph.casillas@rutgers.edu}  
Office: AB 5174  
Office hours: by appointment

**Note**: Readings must be completed *before* the class that occurs 
in the assigned week (i.e., readings assigned for week 2 will be 
discussed *in* the week 2 class, thus they should be read *before*.).

```{r, eval=TRUE, echo=FALSE, cache=FALSE, message=FALSE, warnings=FALSE}
library(RefManageR)
bib <- ReadBib("../bib/span589.bib", check = FALSE)
```







# Week 2: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
ui <- "-"
writeLines(ui); print(bib["wickham2015"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_preface"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch1"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qml_ch1"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

```

### Additional resources

- [Field Guide to the R Ecosystem (highly recommended)](http://fg2re.sellorm.com)
- [Data science and R: How do I start?](https://medium.com/@kierisi/data-science-and-r-how-do-i-start-7a87426e103e)
- [GitHub for the useR](http://happygitwithr.com)
- [Using Git and GitHub](https://biodatascience.github.io/compbio/github.html)
- [Getting help](https://dcl-2017-04.github.io/curriculum/getting-help.html)











# Week 3: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qml_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch3"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```
- [R for excel users](http://rex-analytics.com/r-for-excel-users/)

### Additional resources

- [RMarkdown cheatsheet](https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf)
- [RMarkdown reference](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf)
- [Getting started with RMarkdown](https://www.rstudio.com/resources/webinars/getting-started-with-r-markdown/)
- [ggplot2 cheatsheet](https://www.rstudio.com/wp-content/uploads/2016/11/ggplot2-cheatsheet-2.1.pdf)
- [Secrets to a happy graphing life](http://stat545.com/block016_secrets-happy-graphing.html)
- [A Compendium of Clean Graphs in R](http://shinyapps.org/apps/RGraphCompendium/index.php)









# Week 4: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qml_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch4"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch5"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [The tidyverse style guide](http://style.tidyverse.org)
- [reprex 1](https://dcl-2017-04.github.io/curriculum/reprexes.html)
- [reprex 2](https://github.com/tidyverse/reprex#what-is-a-reprex)
- [Data structure basics](https://dcl-2017-04.github.io/curriculum/data-structure-basics.html)
- [Correlation game](https://gallery.shinyapps.io/correlation_game/)
- [Standardizing and correlations](https://richarddmorey.shinyapps.io/standardizing_and_correlations/)












# Week 5: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass22_ch1"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch6"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch9"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [tidyr tutorial](http://www.jvcasillas.com/tidyr_tutorial/)
- [Tidy data](https://www.jstatsoft.org/article/view/v059i10)
- [Non-tidy data](https://simplystatistics.org/2016/02/17/non-tidy-data/)
- [Creating new variables with mutate and ifelse (advanced)](https://rstudio-pubs-static.s3.amazonaws.com/116317_e6922e81e72e4e3f83995485ce686c14.html#/)











# Week 6: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass57_ch1"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass22_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch8"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch21"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```
- [Slidify tutorial](www.jvcasillas.com/slidify_tutorial/index.html)


### Additional resources

- [Fit-a-line](http://shinyapps.org/showapp.php?app=http://lmpp10e-mucesm.srv.mwn.de:3838/felix/lmfit&by=Felix%20Schönbrodt&title=Find-a-fit!&shorttitle=Find-a-fit!)
- [Simple linear regression game](https://gallery.shinyapps.io/simple_regression/)
- [Bivariate linear regression (shiny)](https://jvcasill.shinyapps.io/shiny_bivariate_regression/)









# Week 7: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass22_ch3"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass57_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```
- [xaringan tutorial 1](https://slides.yihui.name/xaringan/#1)
- [xaringan tutorial 2](http://www.jvcasillas.com/ru_xaringan/slides/index.html#1)



### Additional resources

- [R Markdown presentations](https://dcl-2017-04.github.io/curriculum/rmarkdown-formats.html)
- [Model choices/interactions](https://gallery.shinyapps.io/multi_regression/)
- [Diagnostics for simple linear regression](https://gallery.shinyapps.io/slr_diag/)






# Week 8: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass57_ch5"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass50_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass50_ch4"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```
- [papaja documentation](https://github.com/crsh/papaja): Read documentation, 
install package and play with demo example.


### Additional resources

- [Multicollinearity](https://gallery.shinyapps.io/collinearity/)
- [papaja: Reproducible APA manuscripts with R Markdown (skim)](https://crsh.github.io/papaja_man/)
- [More papaja](https://rpubs.com/YaRrr/papaja_guide)
- [R Markdown with papaja (video pt. 1)](https://www.youtube.com/watch?v=I_HW5Rraqg8)
- [R Markdown with papaja (video pt. 2)](https://www.youtube.com/watch?v=dmB6sHDbs7Q)







# Spring break (highly recommended walk through): 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["r4ds_ch18"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["r4ds_ch19"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```





# Week 9: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass93_ch2"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass93_ch3"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
writeLines(ui); print(bib["qass93_ch4"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [Model choices/interactions](https://gallery.shinyapps.io/multi_regression/)
- [The power of multiple regression](http://sphweb.bumc.bu.edu/otlt/MPH-Modules/QuantCore/QuantCore11-Regression/QuantCore11-Regression4.html)
- [StackOverflow question w/ good answer](https://stats.stackexchange.com/questions/94010/understanding-dummy-manual-or-automated-variable-creation-in-glm)
- [Dummy variables (video)](https://www.youtube.com/watch?v=2s8AwoKZ-UE)







# Week 10: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["qass93_ch5"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [Coding systems](https://stats.idre.ucla.edu/r/library/r-library-contrast-coding-systems-for-categorical-variables/)
- [Coding schemes for categorical variables in regression](http://www.mypolyuweb.hk/~sjpolit/coding_schemes.html)







# Week 11 (exam week): 









# Week 12: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["stat_rethink_ch9"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))

writeLines(ui); print(bib["gelman_hill_ch6"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [Generalised Linear Models in R](https://magesblog.com/post/2015-08-04-generalised-linear-models-in-r/)
- [Shiny GLM](https://jvcasill.shinyapps.io/shiny_glm/)
- [When to use logistic regression](http://logisticregressionanalysis.com/33-when-to-use-logistic-regression/)
- [Why regular regression does NOT work](http://logisticregressionanalysis.com/55-why-regular-regression-does-not-work/)
- [What it (multivariate) logistic regression](http://logisticregressionanalysis.com/86-what-is-logistic-regression/)













# Week 13: 

### Reading

```{r, results='asis', echo=FALSE, eval=TRUE}
writeLines(ui); print(bib["gelman_hill_ch5"], 
                      .opts = list(check.entries = TRUE, 
                                   style = "latex", 
                                   bib.style = "authoryear", 
                                   dashed = TRUE))
```

### Additional resources

- [What a Multivariate Logistic Regression Data Set Looks Like: An Example](http://logisticregressionanalysis.com/303-what-a-logistic-regression-data-set-looks-like-an-example/)
- [A little about logs](http://logisticregressionanalysis.com/110-a-little-about-logs/)
- [About odds and odds ratios](http://logisticregressionanalysis.com/160-about-odds-and-odds-ratios/)
- [Understanding Logistic Regression Output](http://logisticregressionanalysis.com/376-understanding-logistic-regression-output-part1/)
- [Sample sizes](http://logisticregressionanalysis.com/1532-how-big-a-sample-how-many-x-variables/)












